Supporting Information : Effect of copula on extinction risk

### 2019-03-01 MainText.Rmd
summary of results

\listoffigures
\listoftables

@@

 <!--Generating maintext figures-->

 <!--FIG : age structure model results : linear, nonlinear-->
\begin{figure}[!h]
\textbf{ \hspace{5.4 cm} (A) \hspace{4 cm} (B)} \\
\vspace{-0.9 cm}
\begin{center}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_extremetail_linear.pdf}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_extremetail_nonlinear_omg_100.pdf}\\
\caption{Extinction risk from single patch age structured model $(A)$ linear ($\Omega = \infty$) and $(B)$ nonlinear ($\Omega = 100$), fecundity of adults and survival of eggs have either extreme left or extreme right tail dependence, numsims=10000. \label{fig_extrisk_agestr}}
\end{center}
\end{figure}

<!--FIG :  summary : all nonlinear model results for local dispersion : extrisk vs. d-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=15 cm]{./Results/allmodel_ext_risk_local_disp.pdf}
\caption{For each of six nonlinear density-dependence models presented in Table \ref{tab_model_info} extinction risk varies as dispersion-rate ($d$) goes from $0$ to $0.5$ for local dispersion. Last two columns represent extinction risk calculated for bifurcation parameter $(r)$ taken from under-compensatory and over-compensatory regime in deterministic model analog.\label{fig_extrisk_allmodel_localdisp}}
\end{center}
\end{figure}

 <!--FIG : all nonlinear model results with d=0, extrisk vs. r-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=5 cm]{./Results/ricker_scl_1/ricker_extrisk_d0.pdf}
\includegraphics[width=5 cm]{./Results/hassell_scl_1/hassell_extrisk_d0.pdf}\\
\vspace{-0.6 cm}
\includegraphics[width=5 cm]{./Results/msmith_scl_0.8/msmith_extrisk_d0.pdf}
\includegraphics[width=5 cm]{./Results/pennycuick_scl_1/pennycuick_extrisk_d0.pdf}\\
\vspace{-0.6 cm}
\includegraphics[width=5 cm]{./Results/verhulst_scl_0.6/verhulst_extrisk_d0.pdf}
\includegraphics[width=5 cm]{./Results/austinbrewer_scl_0.6/abrewer_extrisk_d0.pdf}\\
\caption{Extinction risk varies with bifurcation parameter $(r)$ for all nonlinear density-dependence models without dispersal, numsims=10000. \label{fig_extrisk_d0}}
\end{center}
\end{figure}

>>>>

@@

# Introduction

objectives:

1) Nature of tail dependence in environmental noise (or in vital rates) affects extinction risk of a population differently.
       - Age structure stochastic matrix model : extrisk of left tail dep. > extrisk of right tail dep.
         (This difference is small, could be explained by Tuljapurkar's approx. for linear model, see discussion)

       - 6 Density-dependence models with extreme tail dep. in noise (local/ global dispersal)
           - extrisk depends on tail dependnece as well as on model parameters (under-compensatory, over-compensatory)
           - Rescue effect ??
           - H0 : switching occurs near rc (without dispersal)

# Methods

# Results

# Discussion

 <!--FIG : age structure model results : linear, nonlinear-->
\begin{figure*}[!h]
\textbf{ \hspace{5.4 cm} (A) \hspace{4 cm} (B)} \\
\vspace{-0.9 cm}
\begin{center}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_extremetail_linear.pdf}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_extremetail_nonlinear_omg_100.pdf}\\
\caption{Extinction risk from single patch age structured $(A)$ linear ($\Omega = \infty$) and $(B)$ nonlinear ($\Omega = 100$) models, fecundity of adults and survival of eggs have either extreme left or extreme right tail dependence, numsims=10000. \label{fig_extrisk_agestr}}
\end{center}
\end{figure*}

<!--FIG :  summary : all nonlinear model results for local dispersion : extrisk vs. d-->
\begin{figure*}[!h]
\begin{center}
\includegraphics[width=15 cm]{./Results/allmodel_ext_risk_local_disp.pdf}
\caption{For each of six nonlinear density-dependence models presented in Table \ref{tab_model_summary} with local dispersal, extinction risk varies as dispersion-rate ($d$) goes from $0$ to $0.5$. Last two columns represent extinction risk calculated for bifurcation parameter $(r)$ taken from under-compensatory and over-compensatory regime of deterministic model analog, respectively.\label{fig_extrisk_allmodel_localdisp}}
\end{center}
\end{figure*}

 <!--FIG : all nonlinear model results with d=0, extrisk vs. r-->
\begin{figure*}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=5 cm]{./Results/ricker_scl_1/ricker_extrisk_d0.pdf}
\includegraphics[width=5 cm]{./Results/hassell_scl_1/hassell_extrisk_d0.pdf}\\
\vspace{-0.6 cm}
\includegraphics[width=5 cm]{./Results/msmith_scl_0.8/msmith_extrisk_d0.pdf}
\includegraphics[width=5 cm]{./Results/pennycuick_scl_1/pennycuick_extrisk_d0.pdf}\\
\vspace{-0.6 cm}
\includegraphics[width=5 cm]{./Results/verhulst_scl_0.6/verhulst_extrisk_d0.pdf}
\includegraphics[width=5 cm]{./Results/austinbrewer_scl_0.6/abrewer_extrisk_d0.pdf}\\
\caption{Transition of higher to lower extinction risk (calculated after $25$ years) for 
the metapopulations affected by extreme left tail dependent noise across
$5$ multiple patches without dispersal ($d=0$), as intrinsic 
growth rate ($r$) goes from under to over-compensatory regime. Opposite trends
was observed with extreme right tail dependent noise.
Error bars represent the standard errors associated with $10000$
simulations for extinction risk computed at each $r$.
\label{fig_extrisk_d0}}
\end{center}
\end{figure*}

<!--Summary tables for 6 nonlinear models used-->
```{r read_tab_model_summary,echo=F, results='asis',message=F}
library(kableExtra)
library(dplyr)
dt<-readRDS("./Results/tab_model_summary.RDS")
knitr::kable(dt, escape=F,
             format="latex",digits=3, align="c",table.env='table*',
             caption = "Summary of six density dependence models considered for each metapopulation patch with local or global dispersal; last three columns indicated equilibrium population value ($P_e$), critical growth rate ($r_c$) where deterministic analog of models showed transition from under- to over-compensatory dynamics and bifurcation parameter ($r_{bf}$) where $P_e$ became unstable from stable steady state, respectively.\\label{tab_model_summary}",
             booktabs=T, linesep = "\\addlinespace"
             )%>%column_spec(c(1,3,5,6),width="1.4cm")%>%kable_styling(latex_options = "basic",position = "center")%>%column_spec(2, width = "3.5 cm")
```

### 2019-03-01 SuppMat.Rmd
summary of results

<!--Ricker model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_local_disp.pdf}\\
\caption{Effect of non-Normal environmental noise copula on extinction risk after 25 years; Ricker model with local dispersion; numlocs=5, numsteps=25, numsims=10000, scl=1 \label{fig_ricker_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--Ricker model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_global_disp.pdf}\\
\caption{Effect of non-Normal environmental noise copula on extinction risk after 25 years; Ricker model with global dispersion; numlocs=5, numsteps=25, numsims=10000, scl=1 \label{fig_ricker_risk_global_disp_scl_1}}
\end{center}
\end{figure}

<!--Hassell model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/hassell_scl_1/hassell_ext_risk_local_disp.pdf}\\
\caption{Effect of non-Normal environmental noise copula on extinction risk after 25 years; Hassell model with local dispersion; numlocs=5, numsteps=25, numsims=10000, scl=1 \label{fig_hassell_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--Hassell model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/hassell_scl_1/hassell_ext_risk_global_disp.pdf}\\
\caption{Effect of non-Normal environmental noise copula on extinction risk after 25 years; Hassell model with global dispersion; numlocs=5, numsteps=25, numsims=10000, scl=1 \label{fig_hassell_risk_global_disp_scl_1}}
\end{center}
\end{figure}

<!--Maynard smith model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_local_disp.pdf}\\
\caption{Effect of non-Normal environmental noise copula on extinction risk after 25 years; Maynard Smith model with local dispersion; numlocs=5, numsteps=25, numsims=10000, scl=0.8. \label{fig_msmith_risk_local_disp_scl_0.8}}
\end{center}
\end{figure}

<!--Maynard smith model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_global_disp.pdf}\\
\caption{Effect of non-Normal environmental noise copula on extinction risk after 25 years; Maynard Smith model with global dispersion; numlocs=5, numsteps=25, numsims=10000, scl=0.8. \label{fig_msmith_risk_global_disp_scl_0.8}}
\end{center}
\end{figure}

<!--Pennycuick model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_local_disp.pdf}\\
\caption{Effect of non-Normal environmental noise copula on extinction risk after 25 years; Pennycuick model with local dispersion; numlocs=5, numsteps=25, numsims=10000, scl=1. \label{fig_risk_local_disp_pennycuick_r_vary_scl_1}}
\end{center}
\end{figure}

<!--Pennycuick model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_global_disp.pdf}\\
\caption{Effect of non-Normal environmental noise copula on extinction risk after 25 years; Pennycuick model with global dispersion; numlocs=5, numsteps=25, numsims=10000, scl=1. \label{fig_risk_global_disp_pennycuick_r_vary_scl_1}}
\end{center}
\end{figure}

<!--Verhulst model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_local_disp.pdf}\\
\caption{Effect of non-Normal environmental noise copula on extinction risk after 25 years; Verhulst model with local dispersion; numlocs=5, numsteps=25, numsims=10000, scl=0.6. \label{fig_risk_local_disp_verhulst_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--Verhulst model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_global_disp.pdf}\\
\caption{Effect of non-Normal environmental noise copula on extinction risk after 25 years; Verhulst model with global dispersion; numlocs=5, numsteps=25, numsims=10000, scl=0.6. \label{fig_risk_global_disp_verhulst_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--Austin brewer model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/austinbrewer_scl_0.6/abrewer_ext_risk_local_disp.pdf}\\
\caption{Effect of non-Normal environmental noise copula on extinction risk after 25 years; Austin-Brewer model with local dispersion; numlocs=5, numsteps=25, numsims=10000, scl=0.6. \label{fig_risk_local_disp_abrewer_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--Austin brewer model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/austinbrewer_scl_0.6/abrewer_ext_risk_global_disp.pdf}\\
\caption{Effect of non-Normal environmental noise copula on extinction risk after 25 years; Austin-Brewer model with global dispersion; numlocs=5, numsteps=25, numsims=10000, scl=0.6. \label{fig_risk_global_disp_abrewer_r_vary_scl_0.6}}
\end{center}
\end{figure}

@@

>>>>

@@

<!--Supp. FIG :  summary : all nonlinear model results for global dispersion : extrisk vs. d-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=15 cm]{./Results/allmodel_ext_risk_global_disp.pdf}
\caption{For each of six nonlinear density-dependence models presented in Table \ref{tab_model_summary} with global dispersal, extinction risk varies as dispersion-rate ($d$) goes from $0$ to $0.5$. Last two columns represent extinction risk calculated for bifurcation parameter $(r)$ taken from under-compensatory and over-compensatory regime of deterministic model analog, respectively.\label{fig_extrisk_allmodel_globaldisp}}
\end{center}
\end{figure}

<!--Supp. FIG : Ricker model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Ricker dynamics with local dispersal; 
numsims=10000, sd=1. \label{fig_ricker_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Ricker model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_global_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Ricker dynamics with global dispersal; 
numsims=10000, sd=1. \label{fig_ricker_risk_global_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Hassell model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/hassell_scl_1/hassell_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Hassell dynamics with local dispersal; 
numsims=10000, sd=1. \label{fig_hassell_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Hassell model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/hassell_scl_1/hassell_ext_risk_global_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Hassell dynamics with global dispersal; 
numsims=10000, sd=1. \label{fig_hassell_risk_global_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Maynard smith model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Maynard Smith dynamics with local dispersal; 
numsims=10000, sd=0.8. \label{fig_msmith_risk_local_disp_scl_0.8}}
\end{center}
\end{figure}

<!--Supp. FIG : Maynard smith model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_global_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Maynard Smith dynamics with global dispersal; 
numsims=10000, sd=0.8. \label{fig_msmith_risk_global_disp_scl_0.8}}
\end{center}
\end{figure}

<!--Supp. FIG : Pennycuick model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Pennycuick dynamics with local dispersal; 
numsims=10000, sd=1. \label{fig_risk_local_disp_pennycuick_r_vary_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Pennycuick model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_global_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Pennycuick dynamics with global dispersal; 
numsims=10000, sd=1. \label{fig_risk_global_disp_pennycuick_r_vary_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Verhulst model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Verhulst dynamics with local dispersal; 
numsims=10000, sd=0.6. \label{fig_risk_local_disp_verhulst_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--Supp. FIG : Verhulst model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_global_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Verhulst dynamics with global dispersal; 
numsims=10000, sd=0.6. \label{fig_risk_global_disp_verhulst_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--Supp. FIG : Austin brewer model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/austinbrewer_scl_0.6/abrewer_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Austin-Brewer dynamics with local dispersal; 
numsims=10000, sd=0.6. \label{fig_risk_local_disp_abrewer_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--Supp. FIG : Austin brewer model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/austinbrewer_scl_0.6/abrewer_ext_risk_global_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Austin-Brewer dynamics with global dispersal; 
numsims=10000, sd=0.6. \label{fig_risk_global_disp_abrewer_r_vary_scl_0.6}}
\end{center}
\end{figure}
